\textit{MSF: Modulated Sub-graph Finder}

### 2018-03-01 MSF_Paper_FA.tex
Update MSF_Paper_FA.tex

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/Tgfb1} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/TGFBstep1}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/TGFBstep2} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/TGFBstep3}
		\caption{}
	\end{subfigure}
	\caption{Overview of \texttt{MSF} process showing the steps to identify the modulated sub-graphs. (a) showing a network of genes with green nodes as genes with \textit{p}-values $< $ 0.05, and blue nodes are genes with \textit{p}-values $>$ 0.05, (b) the genes circled red show the two initial modulated sub-graphs, sub-graph1 found one with M,K,C and the second modulated sub-graph2 S,V,T, (c) shows the modulated sub-graph1 being extended to M,K,C,A,D, (d) shows both the modulated sub-graphs merged with the addition of 3 genes Z,W,P.}
			\end{minipage}
}
\end{figure*}

\begin{figure*}
	\centering
	\fbox{
		\begin{minipage}{17 cm}
	\includegraphics[width=1.4\linewidth]{ModulatesSubPaths/MSFData/Ebola6H/newestMergedNetwork}
	\caption{Shows connected modulated sub-graphs from 6hpi, where nodes are genes and edges are the interactions. The node coloring represents the predefined KEGG pathways referring to the nodes in the legend, the edges are from Reactome. Important genes to EBOV infection as from literature are enlarged in the graph. The signal flow depicted in the graph is explained in the text.}
		\end{minipage}
}
\end{figure*}

\begin{figure*}[p]
	\centering
	\fbox{
		\begin{minipage}{17 cm}
			\includegraphics[width=16cm]{Documents/PhDThesis/MSFPaper/DEGvsMSF2}
			\caption{Graph shows the percentage of DEG analysis genes and MSF identified sub-graph genes recall rates 100 times for the three different time points after the addition of Poisson distributed noise.}
			\label{label}
		\end{minipage}
	}
\end{figure*}

>>>>

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/Tgfb1} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/TGFBstep1}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/TGFBstep2} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/TGFBstep3}
		\caption{}
	\end{subfigure}
	\caption{Overview of \texttt{MSF} process showing the steps to identify the modulated sub-graphs. (a) showing a network of genes with green nodes as genes with \textit{p}-values $< $ 0.05, and blue nodes are genes with \textit{p}-values $>$ 0.05, (b) the genes circled red show the two initial modulated sub-graphs, sub-graph1 found one with M,K,C and the second modulated sub-graph2 S,V,T, (c) shows the modulated sub-graph1 being extended to M,K,C,A,D, (d) shows both the modulated sub-graphs merged with the addition of 3 genes Z,W,P.}
			\end{minipage}
}
\end{figure*}

\begin{figure*}
	\centering
	\fbox{
		\begin{minipage}{17 cm}
	\includegraphics[width=1.4\linewidth]{Git/MSF_Paper/newestMergedNetwork}
	\caption{Shows connected modulated sub-graphs from 6hpi, where nodes are genes and edges are the interactions. The node coloring represents the predefined KEGG pathways referring to the nodes in the legend, the edges are from Reactome. Important genes to EBOV infection as from literature are enlarged in the graph. The signal flow depicted in the graph is explained in the text.}
		\end{minipage}
}
\end{figure*}

\begin{figure*}[p]
	\centering
	\fbox{
		\begin{minipage}{17 cm}
			\includegraphics[width=16cm]{Git/MSF_Paper/DEGvsMSF2}
			\caption{Graph shows the percentage of DEG analysis genes and MSF identified sub-graph genes recall rates 100 times for the three different time points after the addition of Poisson distributed noise.}
			\label{label}
		\end{minipage}
	}
\end{figure*}
